FATE summary results

### 2019-12-11 paper draft.Rmd
Little tweak
Changed jitter

plot.regimes <- rbind(clim.regimes, biol.regimes, ichthyo.regimes)
plot.regimes$jitter <- ifelse(plot.regimes$data.set=="Biology 1972-2019" & plot.regimes$probability>0.99, 1.002, plot.regimes$probability)

@@

ggsave("updated HMM regime plot.png", width = 6, height = 4, units='in)
```

>>>>

plot.regimes <- rbind(clim.regimes, biol.regimes, ichthyo.regimes)
plot.regimes$jitter <- ifelse(plot.regimes$data.set=="Biology 1972-2019" & plot.regimes$probability>0.99, 1.004, plot.regimes$probability)

@@

ggsave("updated HMM regime plot.png", width = 6, height = 4, units='in')
```
